---
title: "part1_try2"
author: "Chemin Bae"
date: '2019 10 18 '
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### Import the dataset

```{r}
sdata_t2=read.csv(file="Startup_Try2.csv",header=TRUE, as.is=T)
sdata_t2[sdata_t2=="No Info"]=NA
sdata_t2[sdata_t2==""]=NA
sdata_t2
```


### Remove variables which have more than 50% of missing value (NA)

```{r}
mis_val=sapply(sdata_t2,function(x)sum(is.na(x)))
percent_mis=as.data.frame(round((mis_val/nrow(sdata_t2))*100,1))
name=row.names(percent_mis)
pcnt_mis_var=cbind(name,percent_mis)
row.names(pcnt_mis_var)=NULL
colnames(pcnt_mis_var)=c("variable","Percent.Missing")
percent_mis
```

```{r}
str(sdata_t2)
```
### Cleaning the variables

convert chr variables to factor or integer variables

```{r}
sdata_t2$Dependent.Company.Status[sdata_t2$Dependent.Company.Status=="Failed"]<-0
sdata_t2$Dependent.Company.Status[sdata_t2$Dependent.Company.Status=="Success"]<-1
sdata_t2$Dependent.Company.Status<-as.factor(sdata_t2$Dependent.Company.Status)

sdata_t2$Age.of.company.in.years<-as.integer(sdata_t2$Age.of.company.in.years)

sdata_t2$Number.of.Investors.in.Seed<-as.integer(sdata_t2$Number.of.Investors.in.Seed)

sdata_t2$Number.of.of.repeat.investors<-as.integer(sdata_t2$Number.of.of.repeat.investors)

sdata_t2$Focus.on.consumer.data.[sdata_t2$Focus.on.consumer.data.=="No"]<-0
sdata_t2$Focus.on.consumer.data.[sdata_t2$Focus.on.consumer.data.=="Yes"]<-1
sdata_t2$Focus.on.consumer.data.<-as.factor(sdata_t2$Focus.on.consumer.data.)

sdata_t2$Machine.Learning.based.business[sdata_t2$Machine.Learning.based.business=="No"]<-0
sdata_t2$Machine.Learning.based.business[sdata_t2$Machine.Learning.based.business=="Yes"]<-1
sdata_t2$Machine.Learning.based.business<-as.factor(sdata_t2$Machine.Learning.based.business)

sdata_t2$Predictive.Analytics.business[sdata_t2$Predictive.Analytics.business=="No"]<-0
sdata_t2$Predictive.Analytics.business[sdata_t2$Predictive.Analytics.business=="Yes"]<-1
sdata_t2$Predictive.Analytics.business<-as.factor(sdata_t2$Predictive.Analytics.business)

sdata_t2$Online.or.offline.venture...physical.location.based.business.or.online.venture.[sdata_t2$Online.or.offline.venture...physical.location.based.business.or.online.venture.=="Offline"]<-0
sdata_t2$Online.or.offline.venture...physical.location.based.business.or.online.venture.[sdata_t2$Online.or.offline.venture...physical.location.based.business.or.online.venture.=="Online"]<-1
sdata_t2$Online.or.offline.venture...physical.location.based.business.or.online.venture.<-as.factor(sdata_t2$Online.or.offline.venture...physical.location.based.business.or.online.venture.)

sdata_t2$Solutions.offered[sdata_t2$Solutions.offered=="No"]<-0
sdata_t2$Solutions.offered[sdata_t2$Solutions.offered=="Yes"]<-1
sdata_t2$Solutions.offered<-as.factor(sdata_t2$Solutions.offered)

sdata_t2$Number.of.Direct.competitors<-as.integer(sdata_t2$Number.of.Direct.competitors)

sdata_t2$Avg.time.to.investment...average.across.all.rounds..measured.from.previous.investment<-as.integer(sdata_t2$Avg.time.to.investment...average.across.all.rounds..measured.from.previous.investment)

sdata_t2$Renown.score<-as.integer(sdata_t2$Renown.score)
```

### Make Logistic model

```{r}
t2=glm(Dependent.Company.Status ~ Age.of.company.in.years + Internet.Activity.Score + Employee.Count + Last.Funding.Amount + Number.of.Investors.in.Seed + Number.of.of.repeat.investors + Focus.on.consumer.data. + Machine.Learning.based.business + Predictive.Analytics.business + Online.or.offline.venture...physical.location.based.business.or.online.venture. + Solutions.offered + Number.of.Direct.competitors + Avg.time.to.investment...average.across.all.rounds..measured.from.previous.investment + Renown.score, data=sdata_t2, family=binomial(link="logit"))
summary(t2)
```

* According to the regression, as the startup company focus on consumer data, the possibility of success become higher. : Its p-value is the lowest.
* As the startup company's internet activity score is high, the possibility of success become high. : Its p-value is lower than 0.05, so this variable is reasonable.
* As the startup company do the business based on machine learning, the possilbity of success "can be" higher. : Its p-value is slightly higher than 0.05., but still this variable is reasonable than other variables.

